%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{xcolor}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{https://cesaralmendarez.com}{\Large Cesar E Almendarez}} &
    \href{mailto:cesarealmendarez@gmail.com}{cesarealmendarez@gmail.com}\\
    \href{https://cesaralmendarez.com}{cesaralmendarez.com} & \href{sms:+18182203266}{(818) 220-3266}
\end{tabular*}


%-----------SUMMARY-----------------
\section{SUMMARY}
Computer Science student eager to jump head first into the software industry. Looking to work on products bringing innovation, quality, and value, while appending to my ever-broadening skill set. All via grit and tenacity towards improvement!

% %-----------EDUCATION-----------------
\section{EDUCATION}
    \resumeSubHeadingListStart
        \resumeSubheading
        {California State University, Los Angeles}{Los Angeles, CA}
        {Bachelor of Science, Computer Science}{Expected May 2025}

        % \resumeItemListStart
        
        %     \resumeItem{Relevant Coursework}
        %         {Programming Paradigms, Web and Internet Programming, Analysis of Algorithms, Multivariable Calculus, Linear Algebra}
                
        % \resumeItemListEnd
              
    \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{PROJECTS}
    \resumeSubHeadingListStart
  
    \resumeSubheading
        {Done Did It}{Jan 2023}
        {iOS To-Do List Application}{\href{https://apps.apple.com/us/app/done-did-it/id6445909068}{\faIcon{app-store-ios} App Store}}
      
        \resumeItemListStart
            \resumeItem{}
                {I launched a productivity app to the Apple App Store. I taught myself and incorporated \textbf{OOP} principles in \textbf{Swift} to establish a solid \textbf{MVC} architecture pattern which enabled dynamic interaction of user generated Lists and Tasks throughout the entire app. I utilized \textbf{Firebase} to rapidly implement phone number authentication, along with the ability for users to save/retrieve their data seamlessly and efficiently.}
            \resumeItem{}
              {There were many instances in which functionality like navigation, notifications, etc, was not able to be customized any further in \textbf{SwiftUI}. To mend these shortcomings, I combed through Apple Developer Documentation and integrated suitable methods in \textbf{UIKit} to achieve such desired custom features.}
            \resumeItem{}
              {Through the completion of this project, I strengthened my confidence in implementing Object Oriented data models, working with \textbf{Xcode}, writing efficient data structures, and gave iOS users an efficient way to organize themselves!}          
              
      \resumeItemListEnd

    \resumeSubheading
        {News Nova}{Dec 2022}
        {Live News Web App}{\href{https://newsnova.vercel.app/}{\faIcon{link} newsnova.vercel.app}}
        
        \resumeItemListStart
            \resumeItem{}
                {I launched a live news web app to \href{https://newsnova.vercel.app}{newsnova.vercel.app}. With my existing skills in \textbf{JavaScript}, I quickly picked up \textbf{TypeScript} to statically type definitions for News Nova's data. I generated Medistack REST API endpoints via StepZen, then accessed them via \textbf{GraphQL} queries all to fetch timely world news data on user request. With Next.js 13, I incorporated navigation, searching, and filtering capabilities that allowed the user to seamlessly find the news they care about. Finally, I made the site beautifully accessible with \textbf{TailwindCSS} and \textbf{HeadlessUI}.}      
                
      \resumeItemListEnd

    \resumeSubheading
        {DeepASL}{Dec 2021}
        {ASL Gesture Classification Program }{\href{https://github.com/cesarealmendarez/DeepASL}{\faIcon{link} GitHub}}
        
        \resumeItemListStart
        
            \resumeItem{}
                {Utilizing \textbf{OpenCV} and \textbf{NumPy},  I developed a \textbf{Python} program that can classify live ASL alphabet hand gestures. The model is able to interpret letters A - Y with reasonable accuracy. I implemented depth perception and hand speed tracking algorithms to make the program as seamless as possible, as a result it has an intuitive understanding as to when a hand is in frame and when to trigger an interpretation. }
              
            \resumeItem{}
              {Purposely refrained from incorporating any machine learning libraries to place an emphasis on learning the core architecture and mathematics that are rudimentary to Convolutional Neural Network models.}   

            \resumeItem{}
              {Open sourced on GitHub so anyone can clone and run on their machine with a webcam!}   
                
      \resumeItemListEnd 

    \resumeSubHeadingListEnd

%--------EMPLOYMENT------------
\section{EMPLOYMENT}
    \resumeSubHeadingListStart
    
    % \resumeSubheading
    %     {EPIC Program at CSULA}{Los Angeles, CA}
    %     {Data Collection and Administration Intern}{\href{https://github.com/cesarealmendarez/DeepASL}{\faIcon{link} Jan 2022 - Present}}
        \resumeSubheading
        {EPIC Program at CSULA}{Los Angeles, CA}
        {Data Collection and Administration Intern}{Jan 2022 - Present}
        
        \resumeItemListStart

            \resumeItem{Data Administration}
              {: Facilitating the generation and reporting of site-wide user data. From user registration to volunteer time reporting, data is recorded and quantified to expedite user onboarding, outreach, tech support, and growth. }   
              
            \resumeItem{Web Developement}
              {: Maintaining and building upon EPIC's {\href{https://www.volunteereasy.com/Site/eagleconnect}{\textbf{Eagle Connect}}} homepage to connect over \textbf{600} active CSULA student users with events and opportunities around their community. Leveraging basic \textbf{HTML} and \textbf{CSS} to add custom content and support accessibility.}          
              
      \resumeItemListEnd
            
    \resumeSubHeadingListEnd
  
%--------LANGUAGES, TECH, INTERESTS------------
\section{SKILLS \& INTERESTS}
    \resumeSubHeadingListStart
    
        \item{
            \textbf{Languages}{: JavaScript, TypeScript, Python, Java, C, Swift, PHP, SQL, GraphQL}
            \hfill
        }

        \item{
            \textbf{Frameworks \& Libraries}{: React, React Native, TailwindCSS, OpenCV, Next.js, SwiftUI, Flask}
        }

        \item{
            \textbf{Other Tech}{: Xcode, GitHub, Firebase, OpenCV, Framer Motion, HeadlessUI}
        }
        
        \item{
            \textbf{Interests}{: Computer Vision, UI/UX, Natural Language Processing, Powerlifting, Long Distance Running}
        }
        
    \resumeSubHeadingListEnd
    
\end{document}
